### 2022-07-25 main/chapter_2ljets.tex
enumerate subsubsections; fix a math title

\subsubsection{Fake/non-prompt estimates in $\twoljets$-electroweak regions}
To validate the Matrix Method estimates in $\twoljets$-electroweak regions
when preparing the search, we plotted and inspected many histograms in
selections designed to enhance the FNP backgrounds.
All of these selections leverage the expected independence of the two leptons
in FNP events --- important backgrounds producing leptons through
$Z\rightarrow \ell^\pm\ell^\mp$ must have leptons of the same flavour and
opposite charge, and those are quite accurately reconstructed.
If one lepton is FNP, however, its charge and flavour should be
independent of the other lepton.
Selections requiring different-flavour or same-charge leptons,
in otherwise $Z$-like scenarios, should therefore be
FNP-enhanced.

>>>>

\subsubsection{%
Estimates in \texorpdfstring{$\twoljets$}{2Ljets}-electroweak regions%
}
To validate the Matrix Method estimates in $\twoljets$-electroweak regions
when preparing the search, we plotted and inspected many histograms in
selections designed to enhance the FNP backgrounds.
All of these selections leverage the expected independence of the two leptons
in FNP events --- important backgrounds producing leptons through
$Z\rightarrow \ell^\pm\ell^\mp$ must have leptons of the same flavour and
opposite charge, and those are quite accurately reconstructed.
If one lepton is FNP, however, its charge and flavour should be
independent of the other lepton.
Selections requiring different-flavour or same-charge leptons,
in otherwise $Z$-like scenarios, should therefore be
FNP-enhanced.
